A survey of HTTP caching options on the open Web

### 2015-01-09 sanity/paper1.tex
key-value caches
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@955 43ef1190-90fd-4dd7-a769-d0121f02b80e
mention DyLDO
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@956 43ef1190-90fd-4dd7-a769-d0121f02b80e

@@

>>>>

The \todo{ref dyldo} Dynamic Linked Data Observatory (DyLDO)
performed, and continue to do so, of parts of the Linked Open Data
Cloud to determine dynamicity characteristics of Linked Data. Caching
is one of their motivations, but they have not published statistics on
HTTP headers.

@@

All Web cache implementations we have studied have cached responses in
the form of a key that identifies a serialized object. For short-term
impact, future work should accept this as an architectural constraint.
